Deciphering the Trends: A Comprehensive Analysis of US Birth Rates and Educational Attainment from 1980 to 2020

### 2024-02-02 outputs/paper/paper.qmd
Test
Simulate and test data

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Deciphering the Trends: A Comprehensive Analysis of US Birth Rates and Educational Attainment from 1980 to 2020"
author: "Jagpreet Singh & Alexander Guarasci"
date: "`r format(Sys.Date(), '%B %d, %Y')`" # This will add the current date
date-format: long
bibliography: references.bib
execute:
  echo: false
format: pdf
fig-pos: "H"
abstract: |
 This study investigates homicide trends in Toronto from 2004 to 2020, utilizing data from OpenDataToronto. The data shows a fluctuating increase in homicide rates over the city, with most homicides occurring in a relatively small subset of neighbourhoods. Additionally, the data shows the prevalence of gun violence, a surprising result in a country known for its strict gun control laws. This research is significant as it provides insights into urban violence in a major Canadian city. It contributes to the understanding of urban crime dynamics in the Greater Toronto Area.

---
